A Cloud Native Approach to Adversarial Robustness of Neural Networks

### 2024-05-20 plots/cifar/aft_comparison.tex
update plots

\begin{table*}
\centering
\caption{Comparison of AFR Models on the CIFAR dataset.}
\label{tab:cifar}
\begin{tabular}{lllrrrr}
\toprule
 & AIC & BIC & Concordance & Test Concordance & ICI & E50 \\
\midrule
Weibull & -1.23e+03 & -1.23e+03 & 0.79 & 0.8 & 0.02 & 0 \\
Cox & -- & -- & 0.8 & 0.8 & 0.01 & 0 \\
Log Logistic & -1.34e+03 & -1.34e+03 & 0.79 & 0.79 & 0.01 & 0 \\
Log Normal & -1.39e+03 & -1.39e+03 & 0.79 & 0.79 & 0.01 & 0 \\
\bottomrule
\end{tabular}
\end{table*}

>>>>

\begin{table*}
\centering
\caption{Comparison of AFR Models on the CIFAR dataset.}
\label{tab:cifar}
\begin{tabular}{lllrrrrrr}
\toprule
 & AIC & BIC & Concordance & Test Concordance & ICI & Test ICI & E50 & Test E50 \\
\midrule
Weibull & -4.87e+03 & -4.87e+03 & 0.8 & 0.79 & 0.01 & 0 & 0 & 0 \\
Cox & -- & -- & 0.8 & 0.79 & 0.03 & 0.02 & 0 & 0 \\
Log Logistic & -5.07e+03 & -5.07e+03 & 0.8 & 0.78 & 0.01 & 0.01 & 0 & 0 \\
Log Normal & -5.27e+03 & -5.27e+03 & 0.8 & 0.78 & 0.01 & 0.01 & 0 & 0 \\
\bottomrule
\end{tabular}
\end{table*}

### 2024-05-20 plots/cifar100/aft_comparison.tex
update plots

\begin{table*}
\centering
\caption{Comparison of AFR Models on the CIFAR100 dataset.}
\label{tab:cifar100}
\begin{tabular}{lllrrrr}
\toprule
 & AIC & BIC & Concordance & Test Concordance & ICI & E50 \\
\midrule
Weibull & -1.11e+03 & -1.11e+03 & 0.78 & 0.76 & 0 & 0 \\
Cox & -- & -- & 0.79 & 0.76 & 0.02 & 0 \\
Log Logistic & -1.2e+03 & -1.2e+03 & 0.78 & 0.77 & 0.01 & 0 \\
Log Normal & -1.24e+03 & -1.24e+03 & 0.79 & 0.77 & 0 & 0 \\
\bottomrule
\end{tabular}
\end{table*}

>>>>

\begin{table*}
\centering
\caption{Comparison of AFR Models on the CIFAR100 dataset.}
\label{tab:cifar100}
\begin{tabular}{lllrrrrrr}
\toprule
 & AIC & BIC & Concordance & Test Concordance & ICI & Test ICI & E50 & Test E50 \\
\midrule
Weibull & -4.19e+03 & -4.19e+03 & 0.77 & 0.75 & 0 & 0 & 0 & 0 \\
Cox & -- & -- & 0.77 & 0.76 & 0.01 & 0.01 & 0 & 0 \\
Log Logistic & -4.49e+03 & -4.49e+03 & 0.77 & 0.75 & 0.02 & 0.01 & 0 & 0 \\
Log Normal & -4.65e+03 & -4.65e+03 & 0.77 & 0.75 & 0 & 0 & 0 & 0 \\
\bottomrule
\end{tabular}
\end{table*}

### 2024-05-20 plots/combined/aft_comparison.tex
update plots

\begin{table*}
\centering
\caption{Comparison of AFR Models on the Combined dataset. The metrics are defined in Sec.~\ref{afr}}
\label{tab:combined}
\begin{tabular}{lrrrrrr}
\toprule
 & AIC & BIC & Concordance & Test Concordance & ICI & E50 \\
\midrule
Weibull & -5.57e+03 & -5.57e+03 & 0.84 & 0.84 & 0 & 0 \\
Log Logistic & -5.71e+03 & -5.71e+03 & 0.85 & 0.84 & 0.01 & 0 \\
Log Normal & -5.85e+03 & -5.85e+03 & 0.84 & 0.84 & 0.01 & 0 \\
\bottomrule
\end{tabular}
\end{table*}

>>>>

\begin{table*}
\centering
\caption{Comparison of AFR Models on the combined dataset.}
\label{tab:combined}
\begin{tabular}{lrrrrrrrr}
\toprule
 & AIC & BIC & Concordance & Test Concordance & ICI & Test ICI & E50 & Test E50 \\
\midrule
Weibull & -2.11e+04 & -2.11e+04 & 0.84 & 0.83 & 0 & 0.01 & 0 & 0 \\
Log Logistic & -2.18e+04 & -2.18e+04 & 0.84 & 0.83 & 0.01 & 0.01 & 0 & 0 \\
Log Normal & -2.25e+04 & -2.25e+04 & 0.84 & 0.83 & 0.01 & 0 & 0 & 0 \\
\bottomrule
\end{tabular}
\end{table*}

### 2024-05-20 plots/mnist/aft_comparison.tex
update plots

\begin{table*}
\centering
\caption{Comparison of AFR Models on the MNIST dataset.}
\label{tab:mnist}
\begin{tabular}{lllrrrr}
\toprule
 & AIC & BIC & Concordance & Test Concordance & ICI & E50 \\
\midrule
Weibull & -1.56e+03 & -1.56e+03 & 0.9 & 0.9 & 0.02 & 0 \\
Cox & -- & -- & 0.9 & 0.89 & 0.03 & 0 \\
Log Logistic & -1.67e+03 & -1.67e+03 & 0.9 & 0.9 & 0.02 & 0 \\
Log Normal & -1.71e+03 & -1.71e+03 & 0.9 & 0.9 & 0.01 & 0 \\
\bottomrule
\end{tabular}
\end{table*}

>>>>

\begin{table*}
\centering
\caption{Comparison of AFR Models on the MNIST dataset.}
\label{tab:mnist}
\begin{tabular}{lllrrrrrr}
\toprule
 & AIC & BIC & Concordance & Test Concordance & ICI & Test ICI & E50 & Test E50 \\
\midrule
Weibull & -5.83e+03 & -5.83e+03 & 0.9 & 0.9 & 0.01 & 0.01 & 0 & 0 \\
Cox & -- & -- & 0.9 & 0.9 & 0.03 & 0.03 & 0 & 0 \\
Log Logistic & -6.1e+03 & -6.1e+03 & 0.9 & 0.91 & 0.02 & 0.02 & 0 & 0 \\
Log Normal & -6.25e+03 & -6.25e+03 & 0.9 & 0.91 & 0.02 & 0.02 & 0 & 0 \\
\bottomrule
\end{tabular}
\end{table*}
